Design, Implementation, and Evaluation of Open Power Quality

### 2020-06-22 09-pilot.tex
Expand on optimizations.

Given that OPQ Boxes were configured to sample at 12 kHz at 2 bytes per sample during the deployment, we can calculate the bounds on raw storage for 16 OPQ Boxes over 3 months without TTL as 3.1 TiB. Figure~\ref{fig:data-management-graph} shows slightly less data as OPQ Boxes were added to the deployment over the course of the month and we did not have all 16 OPQ Boxes recording continuously since the begining of the pilot study.

@@

The top layer of OPQ's information architecture supports adaptive optimization: the ability to analyze previously collected data and use it to change the settings associated with data collection from OPQ Boxes.  One way we used this capability was to identify periodic phenomena, then predict when it was going to occur in future, and then change the settings associated with Boxes to support better data collection during periods in which a power quality anomaly was predicted.

\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black,title=ANTHONY]
Can you provide a "for example" of this with more concrete details, hopefully indicating how this adaptive optimization actually yielded better results?
\end{tcolorbox}

>>>>

Given that OPQ Boxes were configured to sample at 12 kHz at 2 bytes per sample during the deployment, we can calculate the bounds on raw storage for 16 OPQ Boxes over 3 months without TTL as 3.1 TiB. Figure~\ref{fig:data-management-graph} shows slightly less data as the number of OPQ Boxes was not constant during the pilot study (Figure~\ref{fig:active-opq-boxes})

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.75\linewidth]{images/pilot/active-opq-boxes.png}
    \caption{Active OPQ Boxes vs. Time}
    \label{fig:active-opq-boxes}
\end{figure}

@@

The top layer of OPQ's information architecture supports adaptive optimization: the ability to analyze previously collected data and use it to change the settings associated with data collection from OPQ Boxes.

%One way we used this capability was to identify periodic phenomena, then predict when it was going to occur in future, and then change the settings associated with Boxes to support better data collection during periods in which a power quality anomaly was predicted.

Two areas where adaptive optimizations were utilized are identifying periodic phenomena and predictions of future phenomena. Periodic phenomena are PQ related signals that occur at regular intervals. One example of periodic phenomena is a cyclic volage sag that was observed at one of our sensors with a period of about 34 minutes during our pilot study (Figure~\ref{fig:periodic-voltage-sags}). This periodic phenomena not only provided a classification of an interesting pattern, but also helped optimize the OPQ system for capture of future phenomena. Several system wide optimizations are utilized.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{images/pilot/periodic-voltage-sags.png}
    \caption{Detection of Periodic Voltage Sags}
    \label{fig:periodic-voltage-sags}
\end{figure}

First, classified periodic phenomena are used to generate future phenomena. Future phenomena are a prediction of future signals of interest. When a prediction is made, the system will automatically increase sampling fidelity for the predicted sensor during the time window of the prediction. In particular, the measurement rate is increased from 1 measurement per second to 6 measurements per second providing higher fidelity data. Detection thresholds are also decreased, making it more likely that the predicted signal will be observed even if it is of low magnitude.

As an example, Figure~\ref{fig:future-phenomena} shows the percentage of correctly predicted future phenomena as a function of time. The self-optimizing nature of the system allows the system to make more accurate predictions due to acting on more accurate periodic phenomena.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.60\linewidth]{images/pilot/realized-future-phenomena.png}
    \caption{Future Phenomena Prediction Accuracy Over Time}
    \label{fig:future-phenomena}
\end{figure}

Second, the increase in detection sensitivity makes it more likely that sub-threshold signals of interest will be classified. As example, the increased detection sensitivity allowed us to observe and classify a periodic voltage sag that would not have have been detected by our normal classifier due to the small magnitude of the sag. The detection is provided in Figure~\ref{fig:sub-threshold-detection}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.85\linewidth]{images/pilot/subthreshold-signal.png}
    \caption{Sub-threshold Detection}
    \label{fig:sub-threshold-detection}
\end{figure}

This creates a positive feedback loop where as periodic phenomena become more accurate, future phenomena become more accurate. As future phenomena become more accurate, periodic phenomena become more accurate.

%\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black,title=ANTHONY]
%Can you provide a "for example" of this with more concrete details, hopefully indicating how this adaptive optimization actually yielded better results?
%\end{tcolorbox}
